Clustering analysis and statistics

### 2019-08-29 notebooks/Clustering analysis.Rmd

# Patristic distances
Patristic distances were calculated from the core gene alignment SNP tree.
```{r fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
location_data <- read_excel("../data/st_location_data.xlsx") %>%
  select(id, Kommune, Fylke) %>%
  mutate(fyl_id = group_indices(., Fylke),
         kom_id = group_indices(., Kommune)) %>%
  mutate(Location = paste(fyl_id, kom_id, sep = "-")) %>%
  select(id, Location)

@@

@@

# P-value calculations on SNP distances within animal species
The table presents the non-exact p-values based on 1000 iterations of minimum SNP distances to closest isolate within animal species. The figure shows the distribution of the expected values with the observed values for each animal species denoted as an arrow. Red fox results is excluded from the plot as the observed distance values were too high to visualize.
```{r}
# Import distance data
total_dist <- read_delim("../data/snp_dists/final_Roary_gubbins_SNP_dists.tab",
                         delim = "\t") %>%
  rename("isol1" = `snp-dists 0.6.3`)

>>>>

# Patristic distances
Patristic distances were calculated from the core gene alignment SNP tree. The labelled clades are the groups further investigated.
```{r fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
location_data <- read_excel("../data/st_location_data.xlsx") %>%
  select(id, Kommune, Fylke) %>%
  mutate(fyl_id = group_indices(., Fylke),
         kom_id = group_indices(., Kommune)) %>%
  mutate(Location = paste(fyl_id, kom_id, sep = "-")) %>%
  select(id, Location)

@@

\
\
\

**Subclade trees**

@@

# P-value calculations on SNP distances within animal species
The table presents the non-exact p-values based on 1000 iterations of minimum SNP distances to the closest isolate within each animal species. The figure shows the distribution of the expected values with the observed values for each animal species denoted as an arrow. Red fox results is excluded from the plot as the observed distance values were too high to visualize.
```{r}
# Import distance data
total_dist <- read_delim("../data/snp_dists/final_Roary_gubbins_SNP_dists.tab",
                         delim = "\t") %>%
  rename("isol1" = `snp-dists 0.6.3`)
